### 2021-07-15 doc/thesis/chapters/implementation.tex
cocotb

@@

\cite{cocotbDoc}.

>>>>

Multiple different simulators are available on the market, such as Mentor Graphics ModelSim or QuestaSim, Synopsys VCS or the Cadence Simulator.
The issue with most simulators is, that they are subject to a license fee, depending on the required set of features, or simulation speed.\\

However, there are simulators available, that are free to use.
An example therefor is GHDL, which is an analyzer, compiler and simulator for VHDL and is developed as an open-source project.
GHDL translates the VHDL code to a binary file that contains machine code, which can be executed.
This is supported for a all common operating systems such as Linux, Windows and macOS.
The simulator further supports a VPI (Verilog Procedural Interface), which can be used to control the simulator \cite{GHDLDoc}.

@@

The testbench framework cocotb is developed as a free, open-source project.
It can be used to verify VHDL and SystemVerilog RTL code, in combination with an external simulator.
Various different simulators can be used with cocotb - amongst others, GHDL is supported.
The interface that is used to the simulator is the industry-standard VPI.\\

One of the main advantages of cocotb is, that test cases for the respective RTL code are written in the language Python.
It is therefore also called a co-simulation framework.
Using Python provides a large factor of flexibility and possibilities, since it is a comprehensive language, considering all its extension libraries.
Additionally, Python may be more familiar to engineers in comparison to VHDL and thus, writing testbenches is made simpler with cocotb.

The test cases in Python are implemented as coroutines.
By the way, the name cocotb is constructed by the words \textit{CO}routine, \textit{CO}simulation and \textit{T}est\textit{B}ench \cite{cocotbDoc}.\\

Fig.\ref{fig:bd_cocotb_interface_simulator} gives an overview of how cocotb interfaces with a simulator.
The Python test cases are shown as a list of coroutines, which are managed by a scheduler.
This Python code interfaces with the simulator through standard interfaces like VPI.
The block called \textit{GPI} is developed by cocotb and abstracts the different simulator interfaces, such as VPI, VHPI or FLI.
In the simulator, the device under test (DUT) is instantiated.
The RTL simulation itself is managed by the simulators' scheduler.

\includepicture [1.0] [0]  {Block diagram of the interface between cocotb and a simulator \cite{cocotbDoc}.} {bd_cocotb_interface_simulator} {img/draw.io/bd_cocotb_interface_simulator}
